Report

### 2014-11-24 MSLLReport.tex
correct some miss

\documentclass[slidestop,compress,mathserif]{beamer}
\usepackage{setspace}
\usepackage{ragged2e}
\usepackage{biblatex}
\usepackage{algorithm}           
\usepackage{algorithmic}
\bibliography{Domingos}
\let\raggedright=\RaggedRight
%\usepackage[bars]{beamerthemetree} % Beamer theme v 2.2
\usetheme{Antibes} % Beamer theme v 3.0
\usecolortheme{lily} % Beamer color theme
\title{Report}
\author{Cuiyi}
\institute{}

\begin{document}
% coverpage
\begin{frame} % Cover slide
\titlepage
\end{frame}
%section 1 Supervised Learning
\section{Supervised Learning}
%section 1.1 Discriminate Method
    \subsection{Review}
    %review slide
    \begin{frame}[options]
        \frametitle{Discriminate Method Review}

@@

	\end{frame}
	\section{Maximum Entropy Models}
	\begin{frame}
		\frametitle{What is entropy}
		In thermodynamics, entropy (usual symbol $S$) is a measure of the number of specific ways in which a thermodynamic system may be arranged, commonly understood as a measure of disorder.
		$$\Delta = \int\frac{dQ_{rev}}{T}$$
		In information theory, \textbf{Entropy} is a measure of unpredictability of information content. Shannon defined the entropy $H$ of a discrete random variable $X$ with possible values $x1, ..., xn$ and probability mass function P(X) as:
		$$H(X) = E[I(X)] = E[-\ln(P(X))]$$
		Here $I$ is the information content of X.

@@

	\begin{frame}[shrink]
		\frametitle{What is entropy(6)}
		Let's consider
		\begin{eqnarray*}
			&& H(Y)-I(X,Y)  \\
			&=& -\sum_y p(y)\log p(y) - \sum_{x,y}\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_y\left(\sum_x p(x,y)\right)\log p(y) - \sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_{x,y}p(x,y)\log p(y) - \sum_{x,y}\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)} \\
			&=& -\sum_{x,y}p(x,y)\log p(y|x) = H(Y|X)
		\end{eqnarray*}
		According the formula (7):
		$$I(X,Y) = H(X)+H(Y)-H(X,Y)$$
	\end{frame}

	\begin{frame}[shrink]
		\frametitle{Motivating example}
		Suppose we want a model translate English word \textit{in} to French.

@@

	\begin{frame}
		\frametitle{Training data}
		Let's do some form formalization, suppose we have collected a large number of samples $\{(x_1,y_1),(x_2,y_2),\ldots,(x_N,y_N)\}$.
		\newline
		\newline
		In the example we have been considering, each sample would consist of a phrase $x$ containing the words surrounding \textit{in}, together with the translation $y$ of \textit{in}.
		\newline
		\newline
		We can summarize the training example in terms of its \textbf{empirical probability distribution} $\widetilde{p}$,define by
		$$\widetilde{p}(x,y) = \frac{1}{N} \times \mbox{number of times that $(x,y)$ occurs in sample}$$
	\end{frame}

	\begin{frame}
		\frametitle{Features and constraints}
		First, let's consider the definition of \textbf{feature function}
		$$f(x,y)=\left\{
		\begin{array}{ll}
		1  &\mbox{if $x,y$ satisfy some condition}\\
		0  &\mbox{otherwise}
		\end{array}
		\right.
		$$
		In our example we have employed some constraints, but we could also consider statistics which depend on $x$.

		For instance, we might notice that, in the training example, if \textit{April} is the word following \textit{in}, then the translation of in is en with frequency $\frac{9}{10}$.

@@

	\begin{frame}
		\frametitle{The Maximum Entropy Principle(2)}
		Among the models $p\in \mathcal{C}$, the maximum entropy philosophy dictates that we select the distribution which is most uniform, which means we choose $p$ maximizing the entropy
		\begin{equation}
			H(p) = -\sum_{x,y}\widetilde{p}(x,y)p(y|x)\log p(y|x)
		\end{equation}
		With these definition in hand, we can present the principle of maximum entropy
		\begin{equation}
			p^* = \mathrm{arg}\max_{p\in \mathcal{C}} H(p)
		\end{equation} 
		It can be shown that $p^*$ is well defined; that is, there is always a unique model $p^*$ with maximum entropy in any constrained set $\mathcal{C}$ 
	\end{frame}

@@

	\begin{frame}
		\frametitle{Exponential form}
		Consider the minimum problem in dual problem:
		\begin{equation}
			\Psi(\Lambda) = \min_{p\in\mathcal{C}}\mathcal{L}(p,\Lambda) = \mathcal{L}(p_\Lambda,\Lambda),
		\end{equation}
		where
		\begin{equation}
			p_\Lambda = \mathrm{arg}\max_{p\in\mathcal{C}}\Lambda(p,\Lambda).
		\end{equation}

@@

	\begin{frame}
		\frametitle{Exponential form(2)}
		The we use \textbf{Lagrangian multiplier method} to obtain $p_\Lambda$
		\begin{eqnarray*}
			&&\frac{\partial\mathcal{L}(p,\Lambda)}{\partial p(y|x)} \\
			&=& \sum_{x,y}\widetilde{p}(x)(\log p(y|x) +1) - \sum_y\lambda_0 - \sum_{i=1}^{n}\left(\sum_{x,y}\widetilde{p}(x)f_i(x,y)\right)\\
			&=& \sum_{x,y}\widetilde{p}(x)(\log p(y|x) +1) - \sum_x\widetilde{p}(x)\sum_y\lambda_0 - \sum_{x,y}\widetilde{p}(x)\sum_{i=1}^{n}\lambda_i f_i(x,y)\\
			&=& \sum_{x,y}\widetilde{p}(x)(\log p(y|x) +1) - \sum_{x,y}\widetilde{p}(x)\lambda_0 - \sum_{x,y}\widetilde{p}(x)\sum_{i=1}^{n}\lambda_i f_i(x,y)\\
			&=& \sum_{x,y}\left(\log p(y|x) +1 -\lambda_0 -\sum_{i=1}^{n}\lambda_i f_i(x,y) \right)
		\end{eqnarray*}
	\end{frame}

	\begin{frame}
		\frametitle{Exponential form(3)}
		Let $\frac{\partial\mathcal{L}(p,\Lambda)}{\partial p(y|x)}$ be zero, we obtain
		\begin{equation}
			\log p(y|x) +1 -\lambda_0 -\sum_{i=1}^{n}\lambda_i f_i(x,y) = 0,
		\end{equation}
		then
		\begin{equation}
			p(y|x) = e^{\lambda_0-1}\cdot e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}.
		\end{equation}
		According to constraint (17), we obtain
		\begin{equation}
			p_\Lambda = \frac{1}{Z_\Lambda(x)}e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}
		\end{equation}
		where
		\begin{equation}
			Z_\Lambda(x) = \sum_y e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}
		\end{equation}
	\end{frame}

	\begin{frame}[shrink]
		\frametitle{Maximum likelihood}
		Consider the maximum problem in dual problem:
		\begin{equation}
			\max_\Lambda \Psi(\Lambda)
		\end{equation}
		We suppose
		\begin{equation}
			\Lambda^* = \mathrm{arg}\max_\Lambda \Psi(\Lambda),
		\end{equation}
		then we can solve the optimization problem by $p^* = p_\Lambda$.

@@

	\begin{frame}
		\frametitle{Maximum likelihood (2)}
		According to (26), we obtain
		\begin{equation}
			\log p_\Lambda(y|x) = \sum_{i=1}^{n}\lambda_i f_i(x,y) - \log Z_\Lambda(x)
		\end{equation}
		substitute it to $\Psi(\Lambda)$,
		\begin{eqnarray*}
			\Psi(\Lambda) &=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i)-\sum_{x,y}\widetilde{p}(x)p_\Lambda(y|x)\log Z_\Lambda(x) \\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x \widetilde{p}(x)\log Z_\Lambda(x)\sum_y p_\Lambda(y|x)\\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\log Z_\Lambda(x)
		\end{eqnarray*}
	\end{frame}

	\begin{frame}[shrink]
		\frametitle{Maximum likelihood (3)}
		Consider MLE:
		\begin{equation}
			\mathcal{L}_{\widetilde{p}}(p) = \log \prod_{x,y} p(y|x)^{\widetilde{p}(x,y)} = \sum_{x,y}\widetilde{p}(x,y)\log p(y|x)
		\end{equation}
		According (30) we obtain,
		\begin{eqnarray*}
			\mathcal{L}_{\widetilde{p}}(p_\Lambda) &=& \sum_{x,y}\widetilde{p}(x,y)\left(\sum_{i=1}^{n} \lambda_if_i(x,y) - \log Z_\Lambda(x) \right)\\
			&=& \sum_{x,y}\widetilde{p}(x,y)\sum_{i=1}^{n}\lambda_if_i(x,y)-\sum_{x,y}\widetilde{p}(x,y)\log Z_\Lambda(x) \\
			&=& \sum_{i=1}^{n}\lambda_i\left(\sum_{x,y}\widetilde{p}(x,y)f_i(x,y)\right) - \sum_{x,y}\widetilde{p}(x,y)\log Z_\Lambda(x)\\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\log Z_\Lambda(x)
		\end{eqnarray*}
	\end{frame}

@@

	\section{Distance and Divergence}
	\begin{frame}
		\frametitle{Distance}
		\textbf{Distance} satisfies four constraints which \text{Divergence} may no satisfy.
		\begin{itemize}
			\item \textbf{Non-negativity:} $\forall x,y,\quad d(x,y) \ge 0$
			\item \textbf{Non-degeneracy:} $d(x,y)=0 \Leftrightarrow x=y$
			\item \textbf{Symmetry:} $\forall x,y, \quad d(x,y)=d(y,x)$
			\item \textbf{Triangularity:} $\forall x,y,z \quad d(x,z)\leq d(x,y)+d(y,z)$
		\end{itemize}
		\begin{figure}
			\pgfimage[width=4cm]{"image/29.png"}
		\end{figure}

@@

	\begin{frame}
		\frametitle{Distance(2)}
		In the \textbf{Euclidean space} $\mathbb{R}^n$ ,the distance between two point can be given by \textbf{Minkowski distance}.(When p=2, it is equivalent the \textbf{Euclidean distance} and when p=1, it is equivalent to \textbf{Manhattan distance} ) Other distance, based on norms, are sometimes used instead.
		\begin{itemize}
			\item 1-norm distance  $= \sum_{i=1}^{n}|x_i-y_i|$
			\item 2-norm distance  $= \left(\sum_{i=1}^{n}|x_i-y_i|^2\right)^{1/2}$
			\item p-norm distance  $=  \left(\sum_{i=1}^{n}|x_i-y_i|^p\right)^{1/p}$
			\item $\infty$ norm distance $=\lim\limits_{p\rightarrow\infty}\left(\sum_{i=1}^{n}|x_i-y_i|^p\right)^{1/p}$
		\end{itemize}
		If we care about the direction of the data rather than the magnitude, then using the \textbf{cosine distance} is a common approach. 
		$$\cos \theta = \frac{A\cdot B}{\|A\|\|B\|}$$
	\end{frame}

	\begin{frame}
		\frametitle{Distance(3)}
		\textbf{Why is Euclidean distance not a good metric in most situation?}
		\begin{itemize}
			\item Vector length often is not determinant.
			\item Most Problems are in high-dimensional.
			\item Most of the volume of a high-dimensional orange is in the skin, not the pulp.
		\end{itemize}
		\begin{figure}
			\pgfimage[width=3cm ]{"image/30.png"}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Divergence}
	\end{frame}
\end{document}

>>>>

\documentclass[slidestop,compress,mathserif]{beamer}
\usepackage{setspace}
\usepackage{ragged2e}
\usepackage{biblatex}
\usepackage{algorithm}           
\usepackage{algorithmic}
\usepackage{wasysym}
\bibliography{Domingos}
\let\raggedright=\RaggedRight
%\usepackage[bars]{beamerthemetree} % Beamer theme v 2.2
\usetheme{Antibes} % Beamer theme v 3.0
\usecolortheme{lily} % Beamer color theme
\title{Report}
\author{Cuiyi}
\institute{}

\begin{document}
% coverpage
\begin{frame} % Cover slide
\titlepage
You can get this ppt from https://github.com/saiichi/LearnReport
\end{frame}
%section 1 Supervised Learning
\section{Supervised Learning}
%section 1.1 Discriminate Method
    \subsection{Review}
    %review slide
    \begin{frame}[options]
        \frametitle{Discriminate Method Review}

@@

	\end{frame}
	\section{Maximum Entropy Models}
	\subsection{Basic Knowledge}
	\begin{frame}
		\frametitle{What is entropy}
		In thermodynamics, entropy (usual symbol $S$) is a measure of the number of specific ways in which a thermodynamic system may be arranged, commonly understood as a measure of disorder.
		$$\Delta S = \int\frac{dQ_{rev}}{T}$$
		In information theory, \textbf{Entropy} is a measure of unpredictability of information content. Shannon defined the entropy $H$ of a discrete random variable $X$ with possible values $x_1, ..., x_n$ and probability mass function P(X) as:
		$$H(X) = E[I(X)] = E[-\ln(P(X))]$$
		Here $I$ is the information content of X.

@@

	\begin{frame}[shrink]
		\frametitle{What is entropy(6)}
		Let's consider
		\begin{eqnarray*}
			&& H(Y)-I(X,Y)  \\
			&=& -\sum_y p(y)\log p(y) - \sum_{x,y}\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_y\left(\sum_x p(x,y)\right)\log p(y) - \sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_{x,y}p(x,y)\log p(y) - \sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)} \\
			&=& -\sum_{x,y}p(x,y)\log p(y|x) = H(Y|X)
		\end{eqnarray*}
		According the formula (7):
		$$I(X,Y) = H(X)+H(Y)-H(X,Y)$$
	\end{frame}

	\subsection{Modeling}
	\begin{frame}[shrink]
		\frametitle{Motivating example}
		Suppose we want a model translate English word \textit{in} to French.

@@

	\begin{frame}
		\frametitle{Training data}
		Let's do some form formalization, suppose we have collected a large number of samples $\{(x_1,y_1),(x_2,y_2),\ldots,(x_N,y_N)\}$.
		\newline
		\newline
		In the example we have been considering, each sample would consist of a phrase $x$ containing the words surrounding \textit{in}, together with the translation $y$ of \textit{in}.
		\newline
		\newline
		We can summarize the training example in terms of its \textbf{empirical probability distribution} $\widetilde{p}$, define by
		$$\widetilde{p}(x,y) = \frac{1}{N} \times \mbox{number of times that $(x,y)$ occurs in sample}.$$
	\end{frame}

	\begin{frame}
		\frametitle{Features and constraints}
		Now, let's consider the definition of \textbf{feature function}
		$$f(x,y)=\left\{
		\begin{array}{ll}
		1  &\mbox{if $x,y$ satisfy some condition}\\
		0  &\mbox{otherwise}
		\end{array}
		\right.
		$$
		In our example we have employed some constraints, but we could also consider statistics which depend on $x$.

		For instance, we might notice that, in the training example, if \textit{April} is the word following \textit{in}, then the translation of \textit{in} is \textit{en}.

@@

	\begin{frame}
		\frametitle{The Maximum Entropy Principle(2)}
		Among the models $p\in \mathcal{C}$, the maximum entropy philosophy dictates that we select the distribution which is most uniform, which means we choose $p$ maximizing the entropy
		\begin{equation}
			H(p) = -\sum_{x,y}p(x,y)p(y|x)\log p(y|x)
		\end{equation}
		With these definition in hand, we can present the principle of maximum entropy
		\begin{equation}
			p^* = \mathrm{arg}\max_{p\in \mathcal{C}} H(p)
		\end{equation} 
		It can be shown that $p^*$ is well defined; that is, there is always a unique model $p^*$ with maximum entropy in any constrained set $\mathcal{C}$ 
	\end{frame}

@@

	\begin{frame}
		\frametitle{Optimization problem(3)}
		Consider the minimum problem in dual problem:
		\begin{equation}
			\Psi(\Lambda) = \min_{p\in\mathcal{C}}\mathcal{L}(p,\Lambda) = \mathcal{L}(p_\Lambda,\Lambda),
		\end{equation}
		where
		\begin{equation}
			p_\Lambda = \mathrm{arg}\max_{p\in\mathcal{C}}\mathcal{L}(p,\Lambda).
		\end{equation}
		The we use \textbf{Lagrangian multiplier method} to obtain $p_\Lambda$
		\begin{equation}
		\frac{\partial\mathcal{L}(p,\Lambda)}{\partial p(y|x)} 
		=\widetilde{p}(x)(\log p(y|x) +1) - \lambda_0 - \sum_{i=1}^{n}\widetilde{p}(x)f_i(x,y)
		\end{equation}

@@

	\begin{frame}[shrink]
		\frametitle{Optimization problem(4)}

		Let $\frac{\partial\mathcal{L}(p,\Lambda)}{\partial p(y|x)}$ be zero, we obtain
		\begin{equation}
		\log p(y|x) +1 -\lambda_0 -\sum_{i=1}^{n}\lambda_i f_i(x,y) = 0,
		\end{equation}
		then
		\begin{equation}
		p(y|x) = e^{\lambda_0-1}\cdot e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}.
		\end{equation}
		According to constraint (17), we obtain
		\begin{equation}
		p_\Lambda = \frac{1}{Z_\Lambda(x)}e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}
		\end{equation}
		where
		\begin{equation}
		Z_\Lambda(x) = \sum_y e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}
		\end{equation}
	\end{frame}

	\begin{frame}[shrink]
		\frametitle{Optimization problem(5)}
		Consider the maximum problem in dual problem:
		\begin{equation}
			\max_\Lambda \Psi(\Lambda)
		\end{equation}
		We suppose
		\begin{equation}
			\Lambda^* = \mathrm{arg}\max_\Lambda \Psi(\Lambda),
		\end{equation}
		then we can solve the optimization problem by $p^* = p_\Lambda$.

@@

	\begin{frame}
		\frametitle{Optimization problem(6)}
		According to (26), we obtain
		\begin{equation}
			\log p_\Lambda(y|x) = \sum_{i=1}^{n}\lambda_i f_i(x,y) - \log Z_\Lambda(x)
		\end{equation}
		substitute it to $\Psi(\Lambda)$,
		\begin{eqnarray*}
			\Psi(\Lambda) &=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i)-\sum_{x,y}\widetilde{p}(x)p_\Lambda(y|x)\log Z_\Lambda(x) \\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x \widetilde{p}(x)\log Z_\Lambda(x)\sum_y p_\Lambda(y|x)\\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\log Z_\Lambda(x)
		\end{eqnarray*}
	\end{frame}

	\begin{frame}[shrink]
		\frametitle{Maximum likelihood}
		Consider MLE:
		\begin{equation}
			\mathcal{L}_{\widetilde{p}}(p) = \log \prod_{x,y} p(y|x)^{\widetilde{p}(x,y)} = \sum_{x,y}\widetilde{p}(x,y)\log p(y|x)
		\end{equation}
		According (30) we obtain,
		\begin{eqnarray*}
			\mathcal{L}_{\widetilde{p}}(p_\Lambda) &=& \sum_{x,y}\widetilde{p}(x,y)\left(\sum_{i=1}^{n} \lambda_if_i(x,y) - \log Z_\Lambda(x) \right)\\
			&=& \sum_{x,y}\widetilde{p}(x,y)\sum_{i=1}^{n}\lambda_if_i(x,y)-\sum_{x,y}\widetilde{p}(x,y)\log Z_\Lambda(x) \\
			&=& \sum_{i=1}^{n}\lambda_i\left(\sum_{x,y}\widetilde{p}(x,y)f_i(x,y)\right) - \sum_{x,y}\widetilde{p}(x,y)\log Z_\Lambda(x)\\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\log Z_\Lambda(x)
		\end{eqnarray*}
	\end{frame}

@@

	\section{Similarity measure}
	\subsection{Distance}
	\begin{frame}
		\frametitle{Euclidean distance and cosine}
		Strict \textbf{distance} satisfies four constraints while \text{divergence} may no satisfy.
		\begin{itemize}
			\item \textbf{Non-negativity:} $\forall x,y,\quad d(x,y) \ge 0$
			\item \textbf{Non-degeneracy:} $d(x,y)=0 \Leftrightarrow x=y$
			\item \textbf{Symmetry:} $\forall x,y, \quad d(x,y)=d(y,x)$
			\item \textbf{Triangularity:} $\forall x,y,z \quad d(x,z)\leq d(x,y)+d(y,z)$
		\end{itemize}
		\begin{figure}
			\pgfimage[width=3cm]{"image/29.png"}
		\end{figure}

@@

	\begin{frame}
		\frametitle{Euclidean distance and cosine(2)}
		In the \textbf{Euclidean space} $\mathbb{R}^n$ ,the distance between two point can be given by \textbf{Minkowski distance}.(When p=2, it is equivalent the \textbf{Euclidean distance} and when p=1, it is equivalent to \textbf{Manhattan distance} ) Other distance, based on norms, are sometimes used instead.
		\begin{itemize}
			\item 1-norm distance  $= \sum_{i=1}^{n}|x_i-y_i|$
			\item 2-norm distance  $= \left(\sum_{i=1}^{n}|x_i-y_i|^2\right)^{1/2}$
			\item p-norm distance  $=  \left(\sum_{i=1}^{n}|x_i-y_i|^p\right)^{1/p}$
			\item $\infty$ norm distance $=\lim\limits_{p\rightarrow\infty}\left(\sum_{i=1}^{n}|x_i-y_i|^p\right)^{1/p}$
		\end{itemize}
		If we care about the direction of the data rather than the magnitude, then using the \textbf{cosine distance} is a common approach. 
		$$\cos \theta = \frac{A\cdot B}{\|A\|\|B\|}$$
	\end{frame}

	\begin{frame}
		\frametitle{Euclidean distance and cosine(3)}
		\textbf{Why is Euclidean distance not a good metric in most situation?}
		\begin{itemize}
			\item Vector length often is not determinant.
			\item Most Problems are in high-dimensional.
			\item Most of the volume of a high-dimensional orange is in the skin, not the pulp.
		\end{itemize}
	\end{frame}

	\subsection{Divergence}
	\begin{frame}
		\frametitle{Kullback-Leibler Divergence}
		Kullback-Leibler Divergence defines as
		\begin{equation}
			KL(p||p') = \int p(x) \log\frac{p(x)}{p'(x)}dx
		\end{equation}
		\begin{itemize}
			\item[\smiley]  Compatible with maximum likelihood.
			\item[\smiley]  Invariant under input transformation.
			\item[\frownie]  Doesn’t satisfy symmetry and triangularity.
			\item[\frownie]  Sensitive to outliers (due to log and ratio).
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{f-Divergence}
		Definition:
		\begin{equation}
			F(p||p') = \int p'(x)f\left(\frac{p(x)}{p'(x)}\right)dx
		\end{equation}
		where $f$ is convex function such as $f(1)=0$

		Let $f\left(\frac{p(x)}{p'(x)}\right) = \frac{p(x)}{p'(x)}\log \frac{p(x)}{p'(x)}$, then yield the KL-divergence.

		To avoid the log function, let us use $f = \left(\frac{p(x)}{p'(x)}-1\right)^2$. We obtain the \textbf{Pearson (PE) Divergence}
		\begin{equation}
			PE(p||p') = \int p'(x)\left(\frac{p(x)}{p'(x)}-1\right)^2
		\end{equation}
	\end{frame}

	\begin{frame}
		\frametitle{Relative Density Ratio}
		Density ratio $\frac{p(x)}{p'(x)}$ can diverge to infinity. However, Relative density ratio is always bounded:

		\begin{equation}
			\frac{p(x)}{\beta p(x) + (1-\beta)p'(x)} < \frac{1}{\beta} \quad 0\le\beta<1
		\end{equation}
		\begin{figure}
			\pgfimage[width=10cm]{"image/34.png"}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Relative Pearson (rPE) Divergence}
		\begin{equation}
			rPE(p||p') = PE(p||p_\beta) = \int p_\beta(x)\left(\frac{p(x)}{p_\beta(x)}-1\right)^2dx
		\end{equation}
		where
		$$ 0\le\beta<1 \quad p_\beta(x) = \beta p(x) + (1-\beta)p'(x)  $$
		\begin{itemize}
			\item[\smiley]  Compatible with least-squares.
			\item[\smiley]  Invariant under input transformation.
			\item[\smiley]  Robust against outliers.
			\item[\frownie]  Doesn’t satisfy symmetry and triangularity.
			\item[\frownie]  Not clear how to choose $\beta$.
		\end{itemize}
	\end{frame}

	\begin{frame}
		\begin{figure}
			\frametitle{How to choose}
			\pgfimage[width=10cm]{"image/33.png"}
		\end{figure}
	\end{frame}

\end{document}
